### 2023-02-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@dd36a91250906a6bedb7e29e5fa0f81b6bd71ae7 🚀

Another conceptual challenge encountered when using probabilistic food
webs is the prediction of Boolean networks across space. Lets take
\(n \times n\) grid cells each representing a probabilistic food web. If
they contain potential interactions, a single random trial must be
conducted for each pairwise interaction across the region (i.e., we
should have only one random realization of the regional metaweb). On the
contrary, if they represent probabilities of realized interactions, each
food web must be independently sampled (i.e., \(n^2\) independent random
draws). This has direct implications on the spatial scaling of
interactions. For example, let \(N_2\) be another network of area
\(A_2 < A_0\) within \(A_0\) and disjoint from \(N_1\), such as \(N_1\)
and \(N_2\) form \(N_0\) (think of two contiguous cells that together
delineate \(N_0\)). All other things being equal, we should expect the
probability that \(i\) and \(j\) interacts in \(A_0\) to be
\(P_{N_0}(i \rightarrow j) = 1 - (1 - P_{N_1}(i \rightarrow j)) \times (1 - P_{N_2}(i \rightarrow j))\)
if \(N_1\) and \(N_2\) are independently sampled. This also implies that
we should expect interactions to be realized in a certain number of
local networks depending on the probability value, which is not the case
with metawebs. Note that spatial auto-correlation and the concept of
meta-network (i.e., networks of networks) could invalidate the
statistical assumption of independence. Nevertheless, the fundamental
difference in sampling metawebs and local networks stands even when
considering these factors. This difference in sampling further sheds
light on the importance of clearly defining interaction probabilities.
What we consider as a \emph{Bernoulli trial}, when randomly drawing
deterministic networks from probabilistic food webs, depends on our
biological interpretation of these probabilities.

>>>>

Another conceptual challenge encountered when using probabilistic food
webs is the prediction of Boolean networks across space. Lets take
\(n \times n\) grid cells each representing a probabilistic food web. If
they contain potential interactions, a single random trial must be
conducted for each pairwise interaction across the region (i.e., we
should have only one random realization of the regional metaweb). On the
contrary, if they represent probabilities of realized interactions, each
food web must be independently sampled (i.e., \(n^2\) independent random
draws). This has direct implications on the spatial scaling of
interactions. For example, let \(N_1\) and \(N_2\) be networks of area
\(< A_0\) within a bigger area \(A_0\) and disjoint from each other,
such as \(N_1\) and \(N_2\) form \(N_0\) (think of two contiguous cells
that together delineate \(N_0\)). All other things being equal, we
should expect the probability that \(i\) and \(j\) interacts in \(A_0\)
to be
\(P_{N_0}(i \rightarrow j) = 1 - (1 - P_{N_1}(i \rightarrow j)) \times (1 - P_{N_2}(i \rightarrow j))\)
if \(N_1\) and \(N_2\) are independently sampled. This also implies that
we should expect interactions to be realized in a certain number of
local networks depending on the probability value, which is not the case
with metawebs. Note that spatial auto-correlation and the concept of
meta-network (i.e., networks of networks) could invalidate the
statistical assumption of independence. Nevertheless, the fundamental
difference in sampling metawebs and local networks stands even when
considering these factors. This difference in sampling further sheds
light on the importance of clearly defining interaction probabilities.
What we consider as a \emph{Bernoulli trial}, when randomly drawing
deterministic networks from probabilistic food webs, depends on our
biological interpretation of these probabilities.
